SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations

### 2015-08-22 paper.tex
Updates from ShareLaTeX

 \subsection{Step 2}
The second step starts in boht SHIV and DAgger by rolling out the policy $\pi_{\theta_{k}}$ to sample states that are likely to occur under $\theta_{k}$.

@@

Dagger has been experimentally shown to perform well in both simulation and real world
    experiments\cite{}\adnote{cite}. Under a `no regret' assumption, Ross et al.\cite{ross2013learning} furthermore
deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically. For a conservative threshold $\rho$ on risk, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary. However, if $\rho$ is too high, then SHIV will not collect new that that is needed and revert back to the performance of offline methods. We analyze the dependence on $\rho$ in our experimental section. Our results suggest that SHIV is robust to this parameter selection. \adnote{must add this experiment!}

@@

\vspace{-2ex}
\begin{align}\label{eq:decision_func}
g(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
\end{align}

@@

Our corresponding decision function $g:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $$g(\bx) = \sum_i^n
\alpha_i y_i k(\bx_i,\bx) - \rho$$
To compute the $\rho$ term, we leverage the fact that for an optimal solution the
inequalities in Eq. \ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$. Therefore we
can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating} {\color{blue} [-- F:
explain this more --]}.

@@

\subsection{The \acro~algorithm}

Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately
predict the supervisor's control, by means of the thresholded surrogate just discussed.  
% Too vague:
%In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.
%Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  
To reduce the burden on the supervisor, we estimate the training data's quantile level-set for a user-defined threshold
$\nu$ and further modify the corresponding super-levelset estimate by excluding neighborhoods of states that incur a loss
above a threshold $\varepsilon$ chosen by the user.
The user then only provides control input demonstrations for states of trajectory roll-outs that lie outside the
resulting risk-aware quantile super-levelset.

{\color{blue} [-- F: use formal algorithm and explain here instead --]} 
\subsubsection{Step 1}

Similar to DAgger, at iteration $k$, the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$
by solving the optimization problem in Eq. \ref{eq:super_objj}. We then estimate the quantile super-levelset of the
training data state-distribution solving the optimization for the modified One Class SVM using the dataset $\mathcal{D}_k$. 
This yields a decision boundary $g_k(\bx)$, where is $g(\bx)\ge 0$ if a state $\bx$ is to be considered of `low risk' and $-1$ otherwise.

 \subsubsection{Step 2}
 In DAgger, the policy $\pi_{\theta_k}$ is rolled out for a fixed number of time steps, however this could lead to the
 robot entering pathological states that are risky. To prevent this, we terminate the rolled out policy if the risk, is
 above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of providing control inputs for every state, the supervisor is only required to 
 provide demonstrations of control inputs for states for which $g(\bx)=-1$.  These demonstrations are then added to the
 dataset $\mathcal{D}_{k+1}$ and the algorithm returns to Step 1.

We note that the choise of user-defined thresholds $\nu$, $\epsilon$, $r_0$ yield an implicit trade-off
between exploration and exploitation. For large quantile super-levelsets, the robot is confident and asks the
supervisor only rarely for demonstrations. Similarly, large $\varepsilon$ values allow the robot to be tolerant to
incorrectly trained policies with large surrogate loss, while large $r_0$ settings allow the robot to explore risky
areas and obtain more labels from the supervisor in those regions.

>>>>

 \subsection{Step 2}
The second step starts in both SHIV and DAgger by rolling out the policy $\pi_{\theta_{k}}$ to sample states that are likely to occur under $\theta_{k}$.

@@

Dagger has been experimentally shown to perform well in both simulation and real world
    experiments\cite{}\adnote{cite}. Under a `no regret' assumption, Ross et al.\cite{ross2013learning} furthermore
deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically. For a conservative $\sigma$, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary. However, if $\sigma$ is too high, then SHIV will not collect new data that is needed and revert back to the performance of offline methods. We analyze the dependence on $\sigma$ in our experimental section. Our results suggest that SHIV is robust to this parameter selection. \adnote{must add this experiment!}

@@

\vspace{-2ex}
\begin{align}\label{eq:decision_func}
g_{\sigma}(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
\end{align}
\adnote{let's make sure we define $\sigma$ above}

@@

Our corresponding decision function $g_{\sigma}:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $$g_{\sigma}(\bx) = \sum_i^n
\alpha_i y_i k(\bx_i,\bx) - \rho$$
To compute the $\rho$ term, we leverage the fact that for an optimal solution the
inequalities in Eq. \ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$. Therefore we
can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating} {\color{blue} [-- F:
explain this more --]}.

@@

% \subsection{The \acro~algorithm}

% Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately
% predict the supervisor's control, by means of the thresholded surrogate just discussed.  
% % Too vague:
% %In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.
% %Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  
% To reduce the burden on the supervisor, we estimate the training data's quantile level-set for a user-defined threshold
% $\nu$ and further modify the corresponding super-levelset estimate by excluding neighborhoods of states that incur a loss
% above a threshold $\varepsilon$ chosen by the user.
% The user then only provides control input demonstrations for states of trajectory roll-outs that lie outside the
% resulting risk-aware quantile super-levelset.

% {\color{blue} [-- F: use formal algorithm and explain here instead --]} 
% \subsubsection{Step 1}

% Similar to DAgger, at iteration $k$, the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$
% by solving the optimization problem in Eq. \ref{eq:super_objj}. We then estimate the quantile super-levelset of the
% training data state-distribution solving the optimization for the modified One Class SVM using the dataset $\mathcal{D}_k$. 
% This yields a decision boundary $g_k(\bx)$, where is $g(\bx)\ge 0$ if a state $\bx$ is to be considered of `low risk' and $-1$ otherwise.

%  \subsubsection{Step 2}
%  In DAgger, the policy $\pi_{\theta_k}$ is rolled out for a fixed number of time steps, however this could lead to the
%  robot entering pathological states that are risky. To prevent this, we terminate the rolled out policy if the risk, is
%  above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of providing control inputs for every state, the supervisor is only required to 
%  provide demonstrations of control inputs for states for which $g(\bx)=-1$.  These demonstrations are then added to the
%  dataset $\mathcal{D}_{k+1}$ and the algorithm returns to Step 1.

% We note that the choise of user-defined thresholds $\nu$, $\epsilon$, $r_0$ yield an implicit trade-off
% between exploration and exploitation. For large quantile super-levelsets, the robot is confident and asks the
% supervisor only rarely for demonstrations. Similarly, large $\varepsilon$ values allow the robot to be tolerant to
% incorrectly trained policies with large surrogate loss, while large $r_0$ settings allow the robot to explore risky
% areas and obtain more labels from the supervisor in those regions.
